---
title: "Link Table Class Overview"
author: "Tim Whitson"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 6,
  fig.height = 5
)

library(lt)
library(raster)
```

The _LinkTable_ class is designed to improve workflow surrounding the link table, such as rasterization and masking.

To load a link table object you need one of the following:

- A link table version: `LinkTable$from_version()`
- A link table and id raster file: `LinkTable$from_file()`
- A link table and id raster object: `LinkTable$new()`

Using version is the simplest so we will start there:

```{r}
lto <- LinkTable$from_version('future')
```

Now the link table object is loaded:

```{r}
lto
```

The LinkTable object supports most `data.table` bracket operations:

```{r}
lto[NAME_0 == 'Mali' & n > 0]
```

## Rasterizing

You can rasterize the link table easily using the `to_raster()` function:

```{r}
lto$to_raster()

plot(lto$to_raster())

plot(lto[NAME_0 == 'Mali']$to_raster(field = 'ADM2_CODE'))
```

## Masking

The LinkTable objects provides a simple masking function `to_mask()`:

```{r}

lto$to_mask()

plot(lto$to_mask())
```

Let's try a more complex example where we mask Russia, China, and Brazil out of the world raster using only the link table:

```{r}
plot(raster::mask(lto$to_raster(trim_result = FALSE), 
                  lto[NAME_0 == 'Russia' | NAME_0 == 'China' | NAME_0 == 'Brazil']$to_mask(), 
                  inverse = TRUE))
```

## Verifying Raster Coverage

You can also use the LinkTable class to compare a raster with the link table and see if there are any extra or missing pixels. Let's test out a raster with Mali by removing a pixel and adding an extra:

```{r}
mali_raster <- lto[NAME_0 == 'Mali']$to_raster()

first <- which(!is.na(mali_raster[]))[1]
first_na <- which(is.na(mali_raster[]))[1]
mali_raster[first] <- NA
mali_raster[first_na] <- 1

lto[NAME_0 == 'Mali']$verify_raster_coverage(mali_raster)
```